Discrimination and prejudice against women in the workplace ^[Code and data are available at:https://github.com/Faustine123/Newspapers-in-Times-of-Low-Advertising-Revenues]

### 2023-04-21 Output/Paper/Paper.qmd
final commit 2

# Create model summary table
library(modelsummary)
modelsummary(list(model, model2, model3, model4),
             fmt = 2,
             title = "Model Summary of",
             output = 'markdown')
```

>>>>

# Create model summary table
library(modelsummary)
modelsummary(list(model, model2, model3, model4),
             fmt = 2,
             title = "Model Summary of Discrimination and prejudice against women in the workplace",
             output = 'markdown')
```
